\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb, amsmath, amsthm, changepage, graphicx, caption, subcaption}

\graphicspath{{./images/}}

\title{CSC240 Problem Set 1}
\author{Nicolas}

\newcommand{\R}{\mathbb{R}}

\newcommand{\N}{\mathbb{N}}

\newcommand{\Z}{\mathbb{Z}}

\newcommand{\F}{\mathbb{F}}

\newcommand{\C}{\mathbb{C}}

\newcommand{\Q}{\mathbb{Q}}

\newcommand{\andd}{\text{ AND}}

\newcommand{\orr}{\text{ OR}}

\newcommand{\nott}{\text{ NOT}}

\newcommand{\xorr}{\text{ XOR}}

\newcommand{\imp}{\text{ IMPLIES}}

\newenvironment{myproof}
{\begin{proof} \begin{adjustwidth}{3em}{0pt}$ $\par\nobreak\ignorespaces}
{\end{adjustwidth} \end{proof}} 

\begin{document}

\maketitle
\begin{flushleft}

1. a) \\
\bigskip
Exists $n$ st. all indices after $n$ in $S$ are distinct pair-wise. \\
\bigskip
b) \\
\bigskip

If $(S_n)_{n=1}^\infty \in \Z^\infty$ st. $S_n := n$ then the statement is true.

c) \\
\bigskip

If $(S_n)_{n=1}^\infty \in \Z^\infty$ st. $S_n := 1$ then the statement is false.
\\
\bigskip

2. \\
\bigskip
$UScitizen(x) = $ ``Traveller $x$ is a US citizen" corresponds to ``All air travellers who are not US citizens." \\
\bigskip
$FVaccinated(x) = $ ``Traveller $x$ is fully vaccinated" corresponds to ``required to be fully vaccinated." \\
\bigskip
$Proof(x) = $ ``Traveller $x$ has provided proof of vaccination status" corresponds to ``provide proof of vaccination status prior to boarding." \\
\bigskip
$OverTwo(x) = $ ``Traveller $x$'s age is greater than equal to 2" corresponds to ``All airline passengers to the United States ages two years and older." \\
\bigskip
$CovidNeg(x) = $ ``Traveller $x$ provided negative COVID-19 viral test taken within one day" corresponds to ``must provide a negative COVID-19 viral test
taken within one calendar day of travel." \\
\bigskip
$Document(x) = $ ``Traveller $x$ has provided documentation from a licensed health care provider of having recovered from COVID-19 90 days prior" corresponds to ``travellers to the United
States may provide documentation from a licensed health care provider of having
recovered from COVID-19 in the 90 days preceding travel." \\
\bigskip
$Air(x) = $ ``Traveller $x$ is travelling by plane" corresponds to ``Air travellers." \\
\bigskip
$Allowed(x) = (\nott_1 UScitizen(x) \imp_2 (Air(x) \andd_3 FVaccinated(x)) \orr_4 (\nott_5 Air(x) \andd_6 Proof(x)))$ \\
$\andd_7 (OverTwo(x) \imp_8 CovidNeg(x) \orr_9 Document(x))$ \\
\bigskip
$\nott_1$ is because these are only conditions if the traveller is not a US citizen. \\
$\imp_2$ is because if the person is not a US citizen they have to comply with the following two conditions. \\
$\andd_3$ is because air travellers need to be fully vaccinated. \\
$\orr_4$ is because this is the alternative conditional for non US-citizens. \\
$\nott_5$ is because either $Air(x)$ is true or false; this is the false option. \\
$\andd_6$ is because if the traveller is not taking a plane they must follow a different condition. I am just assuming that land ports of entry and ferries are the only other ways of entering the US. \\
$\andd_7$ is because these are the other conditions regardless of the traveller being a US citizen or not. \\
$\imp_8$ is to specify these conditions only to travellers over or equal to the age of two. \\
$\orr_9$ is because there are two conditions. \\
\bigskip
We are also specifying our domain for $Allowed$ to only travellers entering the US, because that is the only situation where a US immigration officer makes sense.

\end{flushleft}

\end{document}