\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb, amsmath, amsthm, changepage}

\title{MAT240 Assignment 1}
\author{Nicolas Coballe}

\newcommand{\bproof}{\begin{proof}
$ $ \\
\begin{adjustwidth}{3em}{0pt}
}

\newcommand{\eproof}{\end{adjustwidth}
\end{proof}}

\begin{document}

\maketitle
\begin{flushleft}

1. a) $|Map(X_n, X_n)| = n^n$ if $n > 0$ or $|Map(X_n, X_n)| = 1$ if $n=0$.

\bproof

Consider the finite, non-empty set $X_n = \{ x_1, x_2, ..., x_n \}$ consisting of $n$ elements and the map $f: X_n \rightarrow X_n$. 
$\forall x_i \in X_n, \exists f(x_i) \in X_n $, and because $X_n$ has a cardinality of $n$, there are only
$n$ different values for $f(x_i)$. Then, there is a choice of $n$, $n$ different times; thus, there are $\underbrace{n \cdot n \cdots n }_\text{$n$ times}$ different possible maps $f: X_n \rightarrow X_n$. Thus the cardinality of $Map(X_n, X_n)$ is $\underbrace{n \cdot n \cdots n }_\text{$n$ times}$, or simply $n^n$.

Considering the case where $n = 0$, $X_n$ is empty, and thus we can easily say that there is one trivial map between the empty set and the empty set, so $|Map(\emptyset , \emptyset )| = 1$.

\eproof

b) $|Bij(X_n, X_n)| = n!$

\bproof

Consider the finite, non-empty set $X_n = \{ x_1, x_2, ..., x_n \}$ consisting of $n$ elements and the bijection $f: X_n \rightarrow X_n$. Suppose $f(x_1) \in X_n$, because $f$ is bijective $f(x_2) \in X_n \setminus \{ f(x_1) \} $. Thus if we continue this process for $n$ iterations we get: $\forall x_i, i>1, x_i \in X_n \setminus \{ f(x_{i-1}) \} \setminus \cdots \setminus \{ f(x_1) \}$ \\
Thus, there is a choice of $(n-i+1)$, $n$ different times ($i$ ranges from $1$ to $n$). This leaves us with $n \cdot (n-1) \cdots 2 \cdot 1$ different possible bijections $f: X_n \rightarrow X_n$. Therefore, the cardinality of $Bij(X_n, X_n)$ is $n \cdot (n-1) \cdots 2 \cdot 1$, or more concisely, $n!$! (This last ``!'' is an exclamation mark and not a second factorial.)

\bigskip
Taking into the consideration when $n = 0$ and $X_n = \emptyset$, there is only one bijection, the identity function. Thus  $Bij(\emptyset , \emptyset ) = 1 = 0!$

\eproof

\newpage

2. a)

\bproof



\eproof

3. a)
\bproof

Consider $ g $ and $ g' $ are both inverses of $f$. \\
\begin{center}
 $\forall x \in X, \ g(f(x)) = x = g'(f(x))$ \\
\end{center}
Since $x$ was chosen arbitrarily, $f(x)$ is just an arbitrary object in $Y$. 
Thus, $ \forall y \in Y, \  g(y) = g'(y)$, and therefore $g = g'$

\eproof

b) $f:\mathbb{R} \rightarrow \mathbb{R}, \ f(x) = x^2$ is not invertible because it is not a bijection. This is because $1 \neq -1$ but $f(1) = f(-1)$ (This is shown by the problem below.)

\bigskip

c) 
\bproof
$\Rightarrow$ \\
We will first prove that $f$ is a surjection. \\
By assumption $\forall y \in Y, \ f(g(y)) = y$ and because $g(y)$ is just an arbitrary element of $X$, this shows that $\forall y \in Y, \ \exists x \in X \ \text{st} \ f(x) = y$ \newline
\\
We will now show that $f$ is an injection. \\
Assume that $f$ is not an injection. \\
Thus, $\exists x, x' \in X$ st $x \neq x'$ and $f(x) = f(x')$ \\
Then $g(f(x)) = g(f(x')) = x = x'$ and thus we have reached a contradiction. \newline
\\
Thus we have proven that $f$ is bijective. \newline
\\
$\Leftarrow$ \\
Because $f:X \rightarrow Y$ is a bijective function, then \\
$\forall y \in Y, \exists ! x \in X$ st $f(x) = y$ \\
Thus we can construct a function $g: Y \rightarrow X$ that maps all $y \in Y$ to the unique $x \in X$ st $f(x) = y$ \\
Thus, by construction $g(f(x)) = x$ and $f(g(y)) = y$

\eproof

\bigskip

d) It does not follow that $f \circ g = I_Y$ \\

\bproof
Consider the function $f:\{ a \} \rightarrow \{ 1,2 \}$ such that $f(a) = 1$ 
and the function $g:\{ 1,2 \} \rightarrow \{ a \}$ such that $g(1) = a$ and $g(2) = a$ \\
Thus $(g \circ f)(a) = a$ and $(g \circ f) = I_X$
But $(f \circ g)(2) = 1$ so $(f \circ g) \neq I_Y$ \\
Thus, we have constructed a counterexample.
\eproof

e) It does follow that $f \circ g = I_Y$ now.

\bproof
If $g \circ f = I_X$ then $f$ is injective because if we assume $f$ is not injective, then we result in the contradiction where $g(f(x)) = g(f(x')) = x = x'$ when $x \neq x'$ \\
Thus $f$ is injective and surjective, making it a bijection, and by part c, this implies that it is invertible and there exists a $g$ st $f \circ g = I_Y$
\eproof


\end{flushleft}
\end{document}